---
title: "MSDS 6306 Unit 4 Homework 4 - Versioning"
author: "Tori Wheelis"
date: "6/5/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
  
# Question 1
  * FiveThirtyEight Data (30 points): Navigate on GitHub to   
  https://github.com/rudeboybert/fivethirtyeight and read README.md. Seriously, it 
  will include everything you need. 
  
## A
  * Install the fivethirtyeight package.
```{r, echo=TRUE}
#install.packages("fivethirtyeight")
```

## B
  * In the listing of Data sets in package ‘fivethirtyeight,’ assign the 
    college_all_ages data set to an object ‘df.’
  
```{r, echo=TRUE}
library(fivethirtyeight)
df <- data.frame(college_all_ages)
```
  
## C
  * Use a more detailed list of the data sets to write out the URL in a comment        to the related news story.
  
```{r, echo=TRUE}
#vignette("fivethirtyeight", package = "fivethirtyeight")
#http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```
  
## D
  * Using R command(s), give the dimensions and column names of this data frame.
  
```{r, echo=TRUE}
dim(df)
```


# Question 2
  * Use your newly assigned data frame for Question 2. 
  
## A
  * Write an R command that gives you the column names of the data frame.  Right       after that, write one that counts the number of columns but not rows.  Hint:       The number should match one of your numbers in Question 1d for dimensions.
    
```{r, echo=TRUE}
colnames(df)

ncol(df)
```

## B
  * Generate a count of each unique major_category in the data frame.  I   
  recommend using libraries to help.  I have demonstrated one briefly in 
  live-session.  To be clear, this should look like a matrix or data frame 
  containing the major_category and the frequency it occurs in the dataset.  
  Assign it to major_count.
    
```{r, echo=TRUE}
library(dplyr)

major_count<-data.frame(table(df$major_category))

major_count
```

## C
  * (To make things easier to read, put par(las=2) before your plot to make the        text perpendicular to the axis.)  Make a barplot of major_count.  Make sure        to label the title with something informative (check the vignette if you           need), label the x and y axis, and make it any color other than grey.  Assign      the major_category labels to their respective bar.  Flip the barplot               horizontally so that bars extend to the right, not upward.  All of these           options can be done in a single pass of barplot(). Note: It’s okay if it’s         wider than the preview pane.

```{r, echo=TRUE}
par(las=2);barplot(major_count$Freq, names.arg = major_count$Var1, horiz = TRUE,xlab="Frequency of Grads polled", sub="y-axis: Major Category of Grads Polled", main="Frequency of Major Categories of College Grads Polled for ROI Study", col="blue")

#ylab is not used to label y-axis and sub is used instead because the bar labels and ylab conflicted and were unreadable. This way everything is still labeled.
```

## D
  * Write the fivethirtyeight data to a csv file.  Make sure that it does not have     row labels.
    
```{r, echo=TRUE}
#write.csv(college_all_ages,'fivethirtyeightCollegeROIStudyData.csv', row.names=FALSE)

#setwd() was used beforehand to place the file in the correct folder, filepath "/Users/toriwheelis/MSDS6306" on my machine.
```
	
	
# Question 3
  * Codebook:

## A
  * Start a new repository on GitHub for your SMU MSDS homework.  On your local       device, make sure there is a directory for Homework at the minimum; you are        welcome to add whatever you would like to this repo in addition to your            requirements here.

## B
 * Create a README.md file which explains the purpose of the repository, the         topics included, the sources for the material you post, and contact information     in case of questions. Remember, the one in the root directory should be            general.  You are welcome to make short READMEs for each assignment           
    individually in other folders.

## C
  * In one (or more) of the nested directories, post your RMarkdown script, HTML      file, and data from ‘fivethirtyeight.’  Make sure that in your README or           elsewhere that you credit fivethirtyeight in some way.

## D
  * In your RMarkdown script, please provide the link to this GitHub so the grader     can see it.
    
```{r, echo=TRUE}
#A. 
#Repository twheelis/msds-6306 was created on github
#filepath /code/msds/msds-6306/github/assignments/homework was created on local drive

#B.
#README files created for the general repo and for this new assignment in folder unit-4

#C.
#RMarkdown script, HTML File, and new README posted in unit-4

#D.
#https://github.com/twheelis/msds-6306
```


# Question 4
  * Submit a separate txt doc of your completed code from Swirl lesson number 15
  
```{r, echo=TRUE}
#Submitted via 2DS and through the Git repository
```