---
title: "Tori's Unit 2 Lecture Assignment Stackloss Skaterplot"
author: "Tori"
date: "5/14/2018"
output: 
  html_document:
    keep_md: true
---

```{r}
summary(stackloss)
```
Interpret Summary
  *The summary command reports the five-number summary, or the minimum, maximum, first and third quartiles, and the mean
  *stackloss data includes variables for air flow, water temperature, acid concentration, and stack loss

```{r}
str(stackloss)
```
Interpret Structure
  *The structure command reports the structure of the called object or data frame. 
  *stackloss data includes 21 observations inside four variables each

```{r}
plot(stackloss$stack.loss, stackloss$Air.Flow,xlab="Stackloss Data", ylab="Airflow Data", main="Skaterplot!!!")
```
Interpret Plot
  *The plot command creates a scatterplot of the specified data on the specified axes
  *In this case, the stackloss variables Air.Flow and stack.loss were plotted, with airflow on the y axis and stackloss on the x axis.
  *The higher the airflow, the higher the stackloss
    *These variables are positively correlated